%-------------------------------------
% LaTeX Resume for Software Engineers
% Author : Leslie Cheng
% License : MIT
%-------------------------------------

\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage[T1]{fontenc}
\usepackage{anyfontsize}
\usepackage{xcolor}

%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Shekhar Prasad Rajak}
\def \subtitle {}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/shekhar-prasad-rajak-9988b626/}
\def \linkedintext {/Shekharrajak}

\def \phoneicon {\faPhone}
\def \phonetext {+91-8142478937}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:shekharrajak@live.com}
\def \emailtext {shekharrajak@live.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/Shekharrajak}
\def \githubtext {/Shekharrajak}

\def \websiteicon {\faGlobe}
\def \websitelink {http://s-hacker.info/}
\def \websitetext {s-hacker.info}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{0D47A1}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{1565C0}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \website {\websiteicon \hspace{3pt}\href{\websitelink}{\websitetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
    linkcolor=blue,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
  \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
    \end{tabular*}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabular*}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]\small{
    \textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
  }
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    {
      \begin{tabular}[c]{l}
        \fontsize{25}{25}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabular*}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabular*}
}

\begin{document}
%-------------------------------------------------- BEGIN HERE --------------------------------------------------

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\linkedin}{\github}{\website}{\phone}{\email}{} % Set the order of items here
\vspace{-10pt} % Set a negative value to push the body up, and the opposite



%-------------------------------------------------- EXPERIENCE --------------------------------------------------
\section{\faPieChart}{Experience}

  \resumeEntryStart
    \resumeEntryTSDL
      {Google Summer of Code - SymPy}{Summer 2016}
      {Student Developer}{}
    \resumeItemListStart
      \resumeItem {Worked on Solvers module of \href{https://github.com/sympy/sympy}{SymPy}  Python library for symbolic mathematics.}
      \resumeItem {Enhanced the features of Solveset module, which ensure the all the solution of equation and system of equations.}
      \resumeItem {Worked on around 55 PRs in \href{https://github.com/sympy/sympy/pulls/Shekharrajak}{SymPy GitHub repository}. Checkout the \href{https://docs.sympy.org/latest/aboutus.html#sympy-development-team}{SymPy development team}.}
      \resumeItem {\href{https://shekharrajak.github.io/gsoc_2016_posts/}{GSoC 2016 report is available in site}, \href{https://summerofcode.withgoogle.com/archive/2016/projects/6728916672708608/}{Project details can be seen at Google Summer of Code site}}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Google Summer of Code - Ruby Science Foundation}{Summer 2017}
      {Student Developer}{}
    \resumeItemListStart
        \resumeItem {Enhanced features and fixed some open issues of \href{https://github.com/SciRuby/daru/}{DaRu} repository.}
        \resumeItem {Designed and built a Ruby library called \href{https://github.com/SciRuby/daru-view/}{daru-view} Data Visualization
in Ruby -- using powerful javascript library - GoogleCharts, HighCharts,
DataTables, D3.js}
        \resumeItem {daru-view can work in any Ruby web application framework, IRuby notebook and simple ruby program as well.}
        \resumeItem {\href{https://shekharrajak.github.io/gsoc_2017_posts/}{GSoC 2017 report link}},
        \href{https://summerofcode.withgoogle.com/archive/2017/projects/5267803426783232/}{Project description on Google Summer of Code site}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {CGI Group}{ 2017 -- 2018}
      {Software Engineer}{Bengaluru, India}
    \resumeItemListStart
      \resumeItem {Designed and built web application - Promotion Automation project.}
      \begin{itemize}
         \item Frontend Angular, Backend - NodeJS, Database - Sql, MongoDB 
         \item Generate BRF document (PDF) for the particular promotion ID. 
         \item Check the difference between latest and previous version promotion.
         \item Searching the latest version of the promotion is easy with UI tool.
         \item One click script generation/testcase/UAT package generation and can seed the data.
       \end{itemize}
      \resumeItem {Led the team as Scrum master, working on \href{http://slides.com/shekharrajak/dd/}{Continuous Deployment Dashboard} project. }
      \begin{itemize}
          \item which is a continuous delivery platform where different teams can view the different stages a product.
          \item Clients have a single view to track progress of their products.
      \end{itemize}
      \resumeItem {Worked with ML team for creating recommendation system(offer/subscription recommendation).}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {Modak Analytics}{2018 -- present}
      {Software Developer}{Hyderabad, India}
    \resumeItemListStart
      \resumeItem {Working on a system for optimal and fast genomic data analysis and
data processing.}
      \resumeItem {Designed and developed Modak Genomics website.}
    \resumeItemListEnd
  \resumeEntryEnd

  
  \resumeEntryStart
    \resumeEntryTSDL
      {Google Summer of Code}{2018 -- 2019}
      {Mentor}{}
    \resumeItemListStart
      \resumeItem {Continue contributing to open source projects and helping new contributors of SymPy and SciRuby. Also mentored students for GSoC 2018 and GSoC 2019}
      \resumeItem {Contributed and mentored \href{https://github.com/Cloud-CV/EvalAI-ngx}{Cloud-CV/EvalAI-ngx} project, which is New Frontend for \href{https://github.com/Cloud-CV/EvalAI}{Cloud-CV/EvalAI} in Latest version of Angular.}
    \resumeItemListEnd
  \resumeEntryEnd


%-------------------------------------------------- PROJECTS --------------------------------------------------
\section{\faFlask}{Projects}

  \resumeEntryStart
    \resumeEntryTD
      {Open Source Projects}{}
    \resumeItemListStart
      \resumeItem {All the Github repository and commits can be seen at \href{https://github.com/Shekharrajak?tab=repositories}{github.com/Shekharrajak/}}
      
      \resumeItem {Blog post designed and developed using Jekyll \href{https://github.com/Shekharrajak/shekharrajak.github.io}{shekharrajak.github.io} and \href{http://s-hacker.info/}{Personal site} }
      
      \resumeItem { \href{https://github.com/Shekharrajak/GithubRepoManager}{Github Repository and Profile Manager}, which uses Github API to fetch the data. This is developed using Angular 4.}
      
      \resumeItem { \href{https://github.com/Shekharrajak?tab=projects}{Projects currently I am working on can be seen at github.com/shekharrajak/projects}}
      
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTD
      {Open Source Contributions}{}
    \resumeItemListStart
      \resumeItem {Maintainer of SciRuby Repositories - \href{https://github.com/SciRuby/daru/}{DaRu} and \href{https://github.com/SciRuby/daru-view/}{daru-view}. Admin of \href{https://github.com/SciRuby/}{SciRuby} for GSoC 2019.
        \begin{itemize}
            \item Responsible for \href{https://github.com/SciRuby/sciruby/wiki/Google-Summer-of-Code-2019-Ideas}{Google Summer of Code - Ruby Science Foundation 2019 application} and Students review & selection.
            
            \item Reviewing PRs and helping/answering new contributors about 
            \href{https://github.com/SciRuby/daru/}{DaRu} gem.
            
            \item New projects and ideas are being added for \href{https://github.com/SciRuby/daru-view/}{daru-view} gem .
        \end{itemize}
      }
      \resumeItem {Maintainer of CloudCV EvalAI-ngx repository.
        \begin{itemize}
            \item Project ideas discussion and PR reviews for \href{https://github.com/Cloud-CV/EvalAI-ngx}{Cloud-CV/EvalAI-ngx}
            
            \item Part of the \href{https://cloudcv.org/team}{GSoC 2019 mentor team}. 
            
        \end{itemize}
      }
      
      \resumeItem {Active in \href{https://github.com/sympy/sympy}{SymPy} and \href{https://github.com/symengine/symengine}{SymEngine} Repository. Helping new contributors and mentored students in Google Summer of Code program.}
      
      \resumeItem {Worked on \href{https://github.com/bundler/bundler/commits?author=Shekharrajak}{4 PRs} in \href{https://github.com/bundler/bundler/}{Bundler Github repository}. Checkout the \href{https://bundler.io/contributors.html}{Bundler Development team}.}
    \resumeItemListEnd
  \resumeEntryEnd


%-------------------------------------------------- PROGRAMMING SKILLS --------------------------------------------------
\section{\faGears}{Skills}
 \resumeEntryStart
  \resumeEntryS{Data Science, Deep Learning, Machine learning} {Daru, daru-view, Pandas, NumPy, Scikit-learn, PyTorch, Keras}
  \resumeEntryS{Web Development } {Angular, NodeJS, Jekyll, Docusaurus}
  \resumeEntryS{Database } {MySql, MongoDB}
  \resumeEntryS{DevOps} {Docker, Git, SVN, Travis CI/CD, Jenkins, Kafka message bus}
  \resumeEntryS{Programming Languages } {C, Cpp, Java, Python, Ruby}
 \resumeEntryEnd

%-------------------------------------------------- EDUCATION --------------------------------------------------
\section{\faGraduationCap}{Education}

  \resumeEntryStart
    \resumeEntryTSDL
      {National Institute of Technology, Warangal}{2013 -- 2017}
      {B.Tech - Computer Science and Engineering}{Warangal, India}
  \resumeEntryEnd


\section{\faFile}{Certificates}
 \resumeEntryStart
  \resumeEntryS{Full Stack Developer }{ \href{https://github.com/Shekharrajak/Resume/blob/master/Certificates/FullStackDeveloper.jpg}{StackRoute Certified} training program on Application design, Design Pattern, Angular, Spring boot, Docker, NoSql and Sql databases.}
  \resumeEntryS{Google Summer of Code } { \href{https://github.com/Shekharrajak/Resume/}{Student Developer - 2016, 2017, Mentor - Since 2018, Org. Admin - 2019} }

 \resumeEntryEnd
 
\section{\faTrophy}{Achievements}
 \resumeEntryStart
  \resumeEntryS{Board topper - Class 12th} {
    \begin{itemize}
        \item Rank 1 in Chhattisgarh Board of Secondary Education (CGBSE) 2012.
        \item Received GOLD Medal for Mathematics stream topper and overall topper.
    \end{itemize}
  }
  \resumeEntryS{Among top 15 student - Class 10th} {
    \begin{itemize}
        \item Chhattisgarh Board of Secondary Education (CGBSE) 2010.
    \end{itemize}
  }
  
  \resumeEntryS{Scholarships} {
    \begin{itemize}
        \item Scholarship by Education minister Chhattisgarh to top 10 students.
        \item Scholarship by Chhattisgarh Government during Under Graduate program(2013-17)
    \end{itemize}
  }
  
 \resumeEntryEnd


\section{}{Extra-Curricular}
  \resumeEntryStart
    \resumeEntryTD
      {}{}
    \resumeItemListStart
      \resumeItem {Member of \href{https://github.com/WSDC-NITWarangal}{Web and Software Development Cell (WSDC) NIT, Warangal}  2015-16.}
      
      \resumeItem {Rated Chess player in chess.com. }
      
      \resumeItem {ISKCON (International Society for Krishna Consciousness) attended 3 sessions in Pune, Chennai, Mangalore.}
      
      \resumeItem {Winner of Vedic Mathematics competition(district level) during school days.}

      \resumeItem {Training at NIT Surathkal on Web Development - 2014 Summer.}      
    \resumeItemListEnd
  \resumeEntryEnd
 

\section{\faBook}{Conferences}
 \resumeEntryStart
  \resumeEntryS{PyCon India 2017} {Organized \href{https://shekharrajak.github.io/blog/Talks/SymPy/PyConIndia-Delhi-2017}{ Workshop on SymPy and SymEngine}. 
  \begin{itemize}
      \item This workshop covered basic to advance features of SymPy.All the tutorial examples are present in \href{https://github.com/Shekharrajak/PyCon-SymPy-SymEngine}{Shekharrajak/PyCon-SymPy-SymEngine} Github repository.
      
      \item Talk about SymEngine - Why SymEngine is created and it's binding with other languages.
      
      \item \href{https://shekharrajak.github.io/PyCon-SymPy-SymEngine/slides-pyconindia2017}{SymPy Slide is present here. }
  \end{itemize}}

  \resumeEntryS{RubyConf India 2018 } {\href{https://shekharrajak.github.io/blog/Talks/SciRuby/RubyConfIndia-Bangalore-2018}{Talk
on SciRuby/daru-view library}}
\begin{itemize}
    \item Presentation on daru-view - how it is useful in Ruby Web application and IRuby notebook as visualization tool.
    \item \href{https://slides.com/shekharrajak/beauty-of-javascript-charts-using-daru-view}{Slide is present on slides.com/shekharrajak}
\end{itemize}

 \resumeEntryEnd
 
\end{document}
